---
title: "Project Overview"
format:
  docx:
    toc: false
params:
  data_path: NA
---

```{r}
#| echo: false
#| include: false
library(dplyr)
library(knitr)
library(flextable)

# Suppress a known xfun::attr() deprecation warning triggered internally by
# knitr::kable() with the installed xfun/knitr version combo; not a content issue.
knitr::opts_chunk$set(warning = FALSE)

# flextable defaults to its own font (Arial) instead of the docx theme font
# (Aptos); match it to the rest of the document.
flextable::set_flextable_defaults(font.family = "Aptos")

record <- readRDS(params$data_path)
info <- record$info
```

# `r record$property_name`

## Summary

```{r}
#| echo: false
phase_followup <- if (is.na(info$phase_id_change)) {
  "\u2014"
} else {
  format(as.Date(info$phase_id_change), "%B %d, %Y")
}

summary_tbl <- tibble::tibble(
  Field = c("Date Added", "Team Lead", "Project Phase", "Phase Set", "PIDs"),
  Value = c(
    format(as.Date(info$date_added), "%B %d, %Y"),
    ifelse(is.na(info$team_lead), "\u2014", info$team_lead),
    ifelse(is.na(info$phase), "\u2014", info$phase),
    phase_followup,
    ifelse(record$pids == "", "\u2014", record$pids)
  )
)

knitr::kable(summary_tbl, col.names = NULL)
```

## Property & Opportunity Overview

`r ifelse(is.na(info$property_description), "No overview available.", info$property_description)`

## Phase Description

`r ifelse(is.na(info$phase_id_description), "No phase description available.", info$phase_id_description)`

## Property Contact(s)

```{r}
#| echo: false
#| results: asis

if (nrow(record$contacts) == 0) {
  cat("No property contacts in database.\n")
} else {
  for (i in seq_len(nrow(record$contacts))) {
    contact <- record$contacts[i, ]

    name <- paste(
      na.omit(c(contact$name_first, contact$name_last)),
      collapse = " "
    )
    if (name == "") {
      name <- "Unknown contact"
    }

    header <- if (
      !is.na(contact$property_contact_description) &&
        contact$property_contact_description != ""
    ) {
      paste0(name, " \u2014 ", contact$property_contact_description)
    } else {
      name
    }

    cat("", header, "\n\n", sep = "")

    details <- c(
      if (!is.na(contact$email) && contact$email != "") {
        paste0("Email: ", contact$email)
      },
      if (!is.na(contact$phone_home) && contact$phone_home != "") {
        paste0("Home: ", contact$phone_home)
      },
      if (!is.na(contact$phone_cell) && contact$phone_cell != "") {
        paste0("Cell: ", contact$phone_cell)
      }
    )

    if (length(details) > 0) {
      cat(paste(details, collapse = " | "), "\n\n")
    }
  }
}
```

## Securement Status

```{r}
#| echo: false
#| results: asis

if (is.na(info$securement_action_description)) {
  cat("No securement status description available.\n")
} else if (is.na(info$date_securement_description)) {
  cat(info$securement_action_description, "\n")
} else {
  cat(
    format(as.Date(info$date_securement_description), "%B %d, %Y"),
    ": ",
    info$securement_action_description,
    "\n",
    sep = ""
  )
}
```

## Internal Communications

```{r}
#| echo: false

if (nrow(record$comms) == 0) {
  knitr::asis_output("No internal communications logged.")
} else {
  record$comms |>
    mutate(date = format(as.Date(date), "%B %d, %Y")) |>
    rename(Date = date, Description = communication_description) |>
    flextable() |>
    width(j = c("Date", "Description"), width = c(1.3, 5.2))
}
```

## Property Contact Communications

```{r}
#| echo: false

if (nrow(record$contact_comms) == 0) {
  knitr::asis_output("No property contact communications logged.")
} else {
  record$contact_comms |>
    mutate(date_contacted = format(as.Date(date_contacted), "%B %d, %Y")) |>
    select(
      Date = date_contacted,
      Purpose = communication_purpose,
      Description = communication_description
    ) |>
    flextable() |>
    width(j = c("Date", "Purpose", "Description"), width = c(1.3, 1.5, 3.7))
}
```

## Action Items

```{r}
#| echo: false

if (nrow(record$actions) == 0) {
  knitr::asis_output("No general action items.")
} else {
  record$actions |>
    mutate(
      Status = if_else(action_complete, "Complete", "Open", missing = "Open"),
      `Due Date` = format(as.Date(due_date), "%B %d, %Y")
    ) |>
    select(
      Status,
      `Team Lead` = team_value,
      `Due Date`,
      Description = action_item_description
    ) |>
    flextable() |>
    width(
      j = c("Status", "Team Lead", "Due Date", "Description"),
      width = c(0.9, 1.3, 1.1, 3.2)
    )
}
```

## Stewardship Concerns

```{r}
#| echo: false
#| results: asis

if (is.na(info$stewardship_concerns) || info$stewardship_concerns == "") {
  cat("None identified at this time.\n")
} else {
  cat(info$stewardship_concerns, "\n")
}
```
